---
title: "Publications Analysis"
author: "Camila Vargas"
date: "2/10/2022"
output: html_document
---

## This script..
Analysis the list of publications bases on research done at Palmyra Atoll. The list of publications so far is based all publications we are aware of (some might be missing).

This analysis was inspired by the folloing publications:
[Trends in ecology and conservation over eight decades](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1002/fee.2320)


## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Load packages
library(tidyverse)
library(lubridate)
library(readxl)
library(tidytext)
library(wordcloud)
library(janitor)
library(tm)
library(here)
library(SnowballC)

```

## Read table
```{r}

# excel_sheets(here("data/palmyra_library_master_20220812.xlsx"))
# 
# all_papers <- read_excel(here("data/palmyra_library_master_20220621.xlsx"), sheet = "palmyra_publications") %>% 
#   clean_names()

all_papers <- read_csv(here("data/palmyra_library_master_20220812.csv")) %>% 
  clean_names()


colnames(all_papers)
```


## Check data

```{r}
str(all_papers)

sort(unique(all_papers$pub_type))
sort(unique(all_papers$publication_year)) ## all good
sort(unique(all_papers$keywords))


```

- pub_type = make "book" and "book chapter" one category. 
- keywords = set to lower

## Fix data

```{r}
correct_all <- all_papers %>% 
  mutate(pub_type = recode(pub_type,
                           "book chapter" = "book"),
         keywords = str_to_lower(keywords),
         title = str_to_title(title))

## check
sort(unique(correct_all$pub_type))

```

## Colors
```{r}
spectral <- c("#d53e4f", "#f46d43", "#fee08b", "#fee08b", "#e6f598", "#abdda4", "#66c2a5", "#3288bd")
```



## Explore

- Percentage by type
```{r}

correct_all %>% 
  group_by(pub_type) %>% 
  tally() %>% 
  mutate(pct = n/279,
         x_axis = "Publications") %>% 
  ggplot(aes(x = x_axis,
             y = pct,
             fill = pub_type))+
  geom_bar(position="stack",
           stat = "identity",
           width = 0.5)+
  coord_flip()+
  scale_y_continuous(labels=scales::percent)+
  scale_fill_manual(values = spectral)+
  theme_classic(base_size = 18)+
  theme(axis.title = element_blank())+
  labs(fill = "Type of Publication")+
  ggtitle("Palmyra Atoll's publications by type")

```



-    Number of publications through the years

```{r}

pubs_year <- correct_all %>% 
  group_by(publication_year) %>% 
  tally() %>% 
  arrange(desc(publication_year))

```


-   Number of publications researcher's have been 1st authors 

```{r}

first_auth <- correct_all %>% 
  mutate(first_author = word(author, 1, sep = ","))

sort(unique(first_auth$first_author))

first_auth_fix <- first_auth %>% 
  mutate(first_author = recode(first_author,
                               "Baumann" = "Baumann-Pickering",
                               "Davis K" = "Davis",
                               "Edwards CB et al." = "Edwards CB",
                               "Edwards" = "Edwards CB",
                               "Mccauley" = "McCauley",
                               "Miller-Ter Kuile A" = "Miller Ter Kuile",
                               "S. Knapp" = "Knapp",
                              "Maragos J.E." = "Maragos")) %>% 
  group_by(first_author) %>% 
  tally()

```

-   Number of publications per author

**needs to be refined, final names are not clean**

```{r}
## All authors
all_authors <- correct_all %>% 
  select(author) %>% 
  unnest_tokens(output = name, 
                input = author) %>% 
  count(name, sort = T)

```

-   Which journals are publications published?

```{r}
journal <- correct_all %>% 
  mutate(journal_title = str_to_title(journal_title),
         journal_title = recode(journal_title,
                "Encyclopedia Of Modern Coral Reefs: Structure, Form And Process" = "Encyclopedia Of Modern Coral Reefs",
                "Journal Of Fish Biology," = "Journal Of Fish Biology",
                "Proceedings Of The Royal Society B: Biological Sciences" = "Proceedings Of The Royal Society B",
               "Proceedings Of The Royal Society" = "Proceedings Of The Royal Society B")) %>% 
  group_by(journal_title) %>% 
  tally() %>% 
  mutate(perc = (n/(sum(n)))*100)
```



## Visualize

-   Color pallets

```{r}

pal_antique <- rev(c("#855C75", "#D9AF6B", "#AF6458", "#736F4C", "#526A83", "#625377", "#68855C", "#9C9C5E", "#A06177", "#8C785D", "#467378", "#7C7C7C"))

pal_prism <- rev(c("#5F4690", "#1D6996", "#38A6A5", "#0F8554", "#73AF48", "#EDAD08", "#E17C05", "#CC503E", "#94346E", "#6F4070", "#994E95", "#666666"))

pal_pastel <-  rev(c("#66C5CC", "#F6CF71", "#F89C74", "#DCB0F2", "#87C55F", "#9EB9F3", "#FE88B1", "#C9DB74", "#8BE0A4", "#B497E7", "#D3B484", "#B3B3B3"))

pal_safe <- c("#88CCEE", "#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499", "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888")

pal_vivid <- c("#E58606", "#5D69B1", "#52BCA3", "#99C945", "#CC61B0", "#24796C", "#DAA51B", "#2F8AC4", "#764E9F", "#ED645A", "#CC3A8E", "#A5AA99")

pal_combo <- c("#F37257", "#F68D5C", "#F4D27A", "#517281", "#7895A2", "#AFC1CC")

```

**Plots**

1. Pubs through the years (2002 and 2022)
    
```{r}

pubs_by_type <- correct_all %>% 
  filter(publication_year > 2002) %>% 
  #        !pub_type %in% c("note", "fact sheet")) %>% 
  # mutate(pub_type = fct_relevel(pub_type, c("paper", "book", "encyclopedia", "PhD thesis", "master thesis", "report"))) %>% 
  ggplot(aes(x = publication_year))+
  #ggplot(aes(x = publication_year, fill = parc_status))+ 
  #geom_bar()+ 
  geom_bar(fill = "#83c4ec")+ ##83c4ec
  scale_x_continuous(breaks = seq(2002,2022, 1))+
  #scale_fill_manual(values = rev(pal_combo))+
  theme_classic(base_size = 18)+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))+
  labs(x = "Year",
       y = "Number of Publications")
       #title = "Publications about Palmyra Atoll")


plot(pubs_by_type)


```

2. Authors count

Top 12 first authors publications

```{r}

first_auth %>% 
  filter(!is.na(first_author)) %>% 
  top_n(5) %>% 
  ggplot(aes(x = reorder(first_author, n),
             y = n))+
  geom_bar(stat="identity",
           fill = "#615f8b")+
  theme_classic()+
  coord_flip()+
  #scale_y_continuous(breaks = seq(0,16, 4))+ 
  labs(x = "Author's Last Name",
       y = "Number of Publications",
       title = "Researchers with most 1st-author publications")

```


3. Journals

```{r}

journal %>% 
  top_n(15) %>% 
  ggplot(aes(x = reorder(journal_title, n),
             y = n))+
  geom_bar(stat="identity",
           fill = "#F4D27A")+
  theme_classic(base_size = 16)+
  coord_flip()+
  scale_y_continuous(breaks = seq(0,25, 5))+ 
  labs(x = "Journal Title",
       y = "Number of Publications",
       title = "Top 10 Journals where Palmyra papers are published")
  
```


 - PARC, No PARC
```{r}
unique(correct_all$parc_status)

parc <- correct_all %>% 
  group_by(parc_status) %>% 
  tally()


```
 

## Word analysis

We want to analyze title, keywords and abstract

1. Titles

```{r}

data("stop_words")

stop_word_vec <- stop_words$word

## Data Frame
title_text <- correct_all %>% 
  select(title) %>% 
  unnest_tokens(word, title) %>% 
  anti_join(stop_words)


title_text_vec <- title_text$word

corpus <- Corpus(VectorSource(title_text_vec))

  # mutate(prural = make_plural(word))
  # count(word, sort = T)

test <- tm_map(corpus, stemDocument)

library(plyr)
library(ggwordcloud)

df <- ldply (test, data.frame)
colnames(df) <- "word_corr"
  
title_count <- df %>% 
  dplyr::count(word_corr) %>% 
  mutate(word_corr = recode(word_corr,
                            "atol" = "atoll",
                            "pacif" = "pacific",
                            "predat" = "predator",
                            "marin" = "marine",
                            "speci" = "species",
                            "communiti" = "community",
                            "variabl" = "variable",
                            "natur" = "nature",
                            "stabl" = "stable")) ## the list is long!


## Plot
title_count %>%
  top_n(15) %>% 
  ggplot(aes(x = reorder(word_corr, n),
             y = n))+
  geom_bar(stat="identity",
           fill = "#f8ab60")+
  theme_classic(base_size = 18)+
  coord_flip()+
  #scale_y_continuous(breaks = seq(0,16, 4))+ 
  labs(x = "Title Words",
       y = "Frequency",
       title = "Top 15 words mentioned in Palmyra's publications title")
  
## Wordcloud

title_count %>% 
  top_n(50) %>% 
  ggplot(aes(label = word_corr, 
           size = n)) +
 geom_text_wordcloud_area() +
  scale_size_area(max_size = 24) +
  theme_minimal()



```


2. Keywords

```{r}

##Table

keyword_text <-  correct_all %>% 
  select(keywords) %>%
  unnest_tokens(word, keywords) %>% 
  anti_join(stop_words) %>%
  mutate(word = recode(word,
                       "reefs" = "reef",
                       "atolls" = "atoll",
                       "predators" = "predator",
                       "sharks" = "shark",
                       "corals" = "corals",
                       "islands" = "island")) %>% 
  dplyr::count(word, sort = T)


## filter out keywords and all that were mention just once

## Plot
keyword_text %>%
  filter(word != "keywords") %>% 
  top_n(25) %>% 
  ggplot(aes(x = reorder(word, n),
             y = n))+
  geom_bar(stat="identity",
           fill = "#96ad8c" )+ #"#7895A2"
  theme_classic(base_size = 18)+
  coord_flip()+
  #scale_y_continuous(breaks = seq(0,16, 4))+ 
  labs(x = "Keywords",
       y = "Count",
       title = "Top 25 Keywords in Palmyra's publications")

```


3. Abstract

**Note:** See how to fix plurals! eg: Coral and Corals

```{r}

## remove stop words from abstract column
abstract_2g <- correct_all %>% 
  select(abstract) %>% #publication_year,
  filter(!is.na(abstract)) %>% 
  # group_by(publication_year) %>% 
  # dplyr::mutate(total_pub_yr = n()) %>% 
  # ungroup() %>% 
  dplyr::mutate(abstract = removeWords(abstract, stopwords("english"))) %>% 
  unnest_tokens(output = ngram, 
                input = abstract,
                token = "ngrams",
                n = 2) %>% 
  dplyr::mutate(ngram = recode(ngram,
                               "coral reefs" = "coral reef",
                               "reef sharks" = "reef shark")) %>% 
  # group_by()
 # group_by(publication_year, total_pub_yr) %>%
  dplyr::count(ngram) %>% 
  filter(!ngram %in% c("our results", "results suggest", "m 2", "m depth", "these results", "we found"))
  
  # dplyr::mutate(fraction = n/total_pub_yr)
  

## just one word - NOT WORKING
abstract_word <- correct_all %>% 
  select(publication_year, abstract) %>% 
  unnest_tokens(output = word, 
                input = abstract) %>% 
  anti_join(stop_words) %>% 
  #group_by(publication_year) %>% 
  count(word)
  

```

**Plot abstract concepts**

```{r}

abstract_2g %>%
  filter(!ngram %in% c("this study", "in contrast", "we also")) %>% 
  top_n(25) %>% 
  ggplot(aes(x = reorder(ngram, n),
             y = n))+
  geom_bar(stat="identity",
           fill = "#7895A2")+ #"#96ad8c"
  theme_classic(base_size = 16)+
  coord_flip()+
  scale_y_continuous(breaks = seq(0,240, 20))+ 
  labs(x = "Concept",
       y = "Frequency",
       title = "Top 25 concepts mentioned in Palmyra's publications abstracts")
  
```



## Searching for management actions key words
- Rat eradication
- Coralimorph
- Shipwreck
- Rainforest realignment


```{r}

mgmt_actions <- correct_all %>% 
  select(title, padl_n, author, doi, abstract) %>% 
  mutate(abstract = str_to_lower(abstract),
         rat_er = ifelse(str_detect(abstract, "rat eradication"), "rat_eradication", NA),
         coral = ifelse(str_detect(abstract, "corallimorph"), "corallim", NA),
         ship = ifelse(str_detect(abstract, "shipwreck"), "shipw", NA)) %>% 
  pivot_longer(cols = c(rat_er, coral, ship),
               names_to = "col",
               values_to = "mention_mgmt_action") %>% 
  select(-col)

mgmt_action_count <- mgmt_actions %>% 
  group_by(mention_mgmt_action) %>% 
  tally()

```


## Search specifically for stresors
**Global**
Climate Change
Ocean Warming
Sea-level rise
Ocean Acidification

**Local**
Invasive species
Marine debris
Pollution
Overfishing/Resource extraction
Habitat Loss (0 found)
Tourism
Sedimentation
Nutrients runoff/fertilization

```{r}

## NOTE: pivot longer duplicates publications
stressors <- correct_all %>% 
  select(title, padl_n, author, doi, abstract) %>% 
  mutate(abstract = str_to_lower(abstract),
         cc = ifelse(str_detect(abstract, "climate change"), "climate change", NA),
         ow = ifelse(str_detect(abstract, "warming ocean"), "ocean warming", NA),
         ow = ifelse(str_detect(abstract, "ocean temperature"), "ocean warming", ow),
         slr = ifelse(str_detect(abstract, "sea level rise"), "sea level rise", NA),
         oa = ifelse(str_detect(abstract, "ocean acidification"), "ocean acidification", NA),
         is = ifelse(str_detect(abstract, "invasive species"), "invasive species", NA),
         pollu = ifelse(str_detect(abstract, "pollution"), "pollution", NA),
         overfish = ifelse(str_detect(abstract, "overfishing"), "overfishing", NA),
         sedi = ifelse(str_detect(abstract, "sedimentation"), "sedimentation", NA),
         tour = ifelse(str_detect(abstract, "tourism"), "tourism", NA),
         fert = ifelse(str_detect(abstract, "fertilization"), "fertilization", NA)) %>% 
   pivot_longer(cols = 6:15,
               names_to = "col",
               values_to = "stressor") %>% 
  select(-col)


stressot_count <- stressors %>% 
  group_by(stressor) %>% 
  tally()


```

