---
title: "Palmyra Papers Table"
author: "Camila Vargas"
date: "10/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(bib2df)
library(tidyverse)
library(janitor)

```


## Read data
```{r}
# df <- bib2df(here::here("data/zotero_oct25.bib")) %>% 
#   clean_names()

zotero <- read_csv(here::here("data/zotero_oct25.csv")) %>% 
  clean_names() %>% 
  select(title, publication_year, author, publication_title, doi, url, date, journal_abbreviation)


masters <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTzUCO3Q2_b7uFlUp_eVCAx0Ss1RrgSWyksX8sTLqjmBEKmsiUM0S_kX2ZuxQJArQ/pub?gid=1022795869&single=true&output=csv") %>% 
  clean_names()


parc_ref <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTzUCO3Q2_b7uFlUp_eVCAx0Ss1RrgSWyksX8sTLqjmBEKmsiUM0S_kX2ZuxQJArQ/pub?gid=2073943422&single=true&output=csv") %>% 
  clean_names() %>% 
  mutate(parc_number = str_extract(parc_ref, "(?<=\\{).+"),
         parc_number = str_remove(parc_number, "\\}"),
         parc_number = str_remove(parc_number, "\\)"),
         parc_number = str_remove(parc_number, "\\.") %>% str_replace_all(., fixed(" "), "")) ## removes all spaces inside the string

```



## New Master Table
It is important to add information such as first author, year of the publication, and reference.

```{r}
master_complete <- masters %>% 
  left_join(parc_ref, by = "parc_number")


parc_ref_list <- parc_ref %>% 
  select(parc_number) %>% 
  pull()


check <- master_complete %>% 
  filter(parc_number %in% parc_ref_list)

```


## Match master and Zotero

```{r}

matching_titles <- master_complete %>% 
  left_join(zotero, by = "title") %>% 
  arrange(parc_number)

```

In Zotero we have 165 references
In our Master table we have 191 references
An only 87 match in title.
Note: title has to be exactly the same for them to match

## Export new master

```{r}
write_csv(matching_titles, here::here("master_complete_1102.csv"))

```



## Authors list

Create a list with all authors that have published at least one paper on Palmyra
```{r}

authors <- c(paste0("author_", 1:20))

zotero_list <- csv %>% 
  select(item_type, publication_year, title, author, journal = publication_title, doi, url, manual_tags, abstract = abstract_note) %>% 
  mutate(zotero_id = 1:n()) %>% 
  separate(author, authors, sep = ";")

```


```{r}
count_per_author <- zotero %>% 
  group_by(author_1) %>% 
  tally()


```

