---
title: "Palmyra Papers Table"
author: "Camila Vargas"
date: "10/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(bib2df)
library(tidyverse)
library(janitor)

```


## Read data
```{r}
# df <- bib2df(here::here("data/zotero_oct25.bib")) %>% 
#   clean_names()

zotero_raw <- read_csv(here::here("data/zotero_oct25.csv"))
  
zotero <- zotero_raw %>%
  clean_names() %>% 
  mutate(title = tolower(title)) %>% 
  select(title, item_type, publication_year, author, publication_title, doi, url, date, abstract_note)


masters <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTzUCO3Q2_b7uFlUp_eVCAx0Ss1RrgSWyksX8sTLqjmBEKmsiUM0S_kX2ZuxQJArQ/pub?gid=1022795869&single=true&output=csv") %>% 
  clean_names()


parc_ref <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTzUCO3Q2_b7uFlUp_eVCAx0Ss1RrgSWyksX8sTLqjmBEKmsiUM0S_kX2ZuxQJArQ/pub?gid=2073943422&single=true&output=csv") %>% 
  clean_names() %>% 
  mutate(parc_number = str_extract(parc_ref, "(?<=\\{).+"),
         parc_number = str_remove(parc_number, "\\}"),
         parc_number = str_remove(parc_number, "\\)"),
         parc_number = str_remove(parc_number, "\\.") %>% str_replace_all(., fixed(" "), "")) ## removes all spaces inside the string

```



## New Master Table
It is important to add information such as first author, year of the publication, and reference.

```{r}
master_complete <- masters %>% 
  left_join(parc_ref, by = "parc_number") %>% 
  mutate(title = tolower(title))


parc_ref_list <- parc_ref %>% 
  select(parc_number) %>% 
  pull()


check <- master_complete %>% 
  filter(parc_number %in% parc_ref_list)

```


## Match master with Zotero

```{r}

matching_titles <- master_complete %>% 
  inner_join(zotero, by = "title") %>%
  mutate(title = str_to_title(title))

```

## Export new master

```{r}

write_csv(matching_titles, here::here("intermediate_files/matching_title.csv"))

```


## Match Zotero with Masters

```{r}

zotero_no_master <- zotero %>% 
  anti_join(master_complete, by = "title")
  # left_join(master_complete, by = "title") %>% 
  # filter(is.na(id))

write_csv(zotero_no_master, here::here("intermediate_files/zotero_no_master.csv"))

master_no_zotero <- master_complete %>% 
  anti_join(zotero, by = "title")

```



In Zotero we have 165 references
In our Master table we have 191 references
An only 87 match in title.
78 papers in Zotero do not match with titles in Master

Note: title has to be exactly the same for them to match




## Authors list

Create a list with all authors that have published at least one paper on Palmyra
```{r}

authors <- c(paste0("author_", 1:20))

zotero_list <- csv %>% 
  select(item_type, publication_year, title, author, journal = publication_title, doi, url, manual_tags, abstract = abstract_note) %>% 
  mutate(zotero_id = 1:n()) %>% 
  separate(author, authors, sep = ";")

```


```{r}
count_per_author <- zotero %>% 
  group_by(author_1) %>% 
  tally()


```

