---
title: "Adding web search papers"
author: "Camila Vargas"
date: '2022-06-24'
output: html_document
---

**Data:** Downloaded from the Web of Knowledge after searching for Palmyra Atoll in all fields on June 24, 2022.

[WOK Query link here](https://www.webofscience.com/wos/woscc/summary/5612105c-1fa9-424a-8937-6eacfdc459a0-3fe3e2a6/recently-added/1)

_Note:_ this query updates with time. If you open this link WOK will provide the most updated search of Palmyra* Atoll* (all fields). So, this link will likely not match out downloaded data because new publications might have been added after 2022-06-24.

**This script:** Reads the list downloaded form WOK to be able to compare with what we have in our master spreadsheet. Ultimately add missing publications to have a complete list.


```{r setup, include=FALSE}

if (!require(librarian)) {
  install.packages("librarian")
  library(librarian)
}

## Load libraries
librarian::shelf("tidyverse",
                 "janitor", #simple functions for examining and cleaning dirty data
                 "here", # #creates paths relative to the top-level directory
                 "readxl") #reads xlsx files

```


## Read data


```{r}
wok_all <- read_excel(here::here("data/webofknowlege_20220624.xls")) %>% 
  clean_names() %>% 
  mutate(wok_id = paste0("wok_", 1:n()))


master_all <-  read_excel(here("data/palmyra_library_master_20220712.xlsx"), sheet = "palmyra_publications") %>% 
  clean_names()


range(wok_all$publication_year, na.rm = T)##2003 to 2022

```

## Using the data we need

```{r}
wok_title_doi <- wok_all %>% 
  select(wok_title = article_title, wok_auth = authors, doi, wok_id) %>% 
  mutate(wok_title = str_to_lower(wok_title))
  
  
master_title_doi <- master_all %>% 
  select(m_title = title, m_auth = author, doi) %>% 
  mutate(m_id = paste0("master_", 1:n()),
         m_title = str_to_lower(m_title),
         doi = str_remove(doi, "doi.org/"))

```


## Combine
Joining by DOI is a more reliable connector between the two data sets. Note that some entries in the Master xlsx do not have DOI. This are either thesis, encyclopedias, book chapters in some cases or a couple of papers that do not have an DOI associated to them.
All entries without a DOI do not apear in the WOK list.

```{r}
both <- wok_title_doi %>% 
  full_join(master_title_doi, by = "doi")

only_wok <- both %>% 
  filter(is.na(m_id))
  
```

There are 89 publications that apparently are not on our list.

### Next steps

#### 1. Build a data frame with all the necessary information, matching the master structure as closely as possible

```{r}
## vector with wok_id that needs to be added to master
vec_wok_id <- only_wok %>% 
  select(wok_id) %>% 
  pull()


missing_wok <- wok_all %>% 
  filter(wok_id %in% vec_wok_id)

wok_to_master <- missing_wok %>% 
  #select(-author_full_names, -issn, -volume, -issue) %>% 
  rename( title = article_title,
          pub_location = doi_link,
         journal_title = source_title,
         author = authors) %>% 
  mutate(transfered_to_zotero_online = "",
         padl_n = "",
         pub_type = "paper",
         parc_status = "NO PARC",
         parc_number = "-",
         lib_status = "",
         data_link = "",
         reference = "",
         keywords = "",
         notes = "",
         address_mgmt_action_which_one = "") %>% 
  select(transfered_to_zotero_online, padl_n, title, pub_type, parc_status, parc_number, lib_status, parc_number, lib_status, pub_location, data_link, reference,   publication_year, author, journal_title, doi, abstract, keywords, notes, address_mgmt_action_which_one)


write_csv(wok_to_master, here::here("exports/wok_papers_missing_20220624.csv"))

```


#### 2. Check and make sure all 89 publications are actually not in the masters

**PUBLICATIONS TITLE THAT IS IN MASTER**
- Diel temperature and pH variability scale with depth across diverse coral reef habitats
- Cryptic species obscure introduction pathway of the blue Caribbean sponge (Haliclona (Soestella) caerulea), (order: Haplosclerida) to Palmyra Atoll, Central Pacific

Only two papers in the missing wok list were found in the master. This means there are 87 publications we need to add to our list.


#### 3. Chek if all missing wok are actually relevant to Palmyra,sAssign a padl id to all wok publications, and fill in missng information, then add to Zotero

#### 4. Add most recent publication in WOK that are not considered in our 2022-06-24 download





